Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-06-29 paper/Draft.tex
finalized ir graphs for whole period

\begin{figure}[ht]
	\centering
	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks_nmp.png}  
	\includegraphics[width=6cm,height=3cm]{figures/CPIAU_ashocks.png} \\
	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks_nmp.png} 
	\includegraphics[width=6cm,height=3cm]{figures/PCEPI_ashocks.png}  \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp.png} 
	\includegraphics[width=6cm]{figures/SPFFE_ashocks.png} \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} \\
	\smallskip 
	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks_nmp.png} 
	\includegraphics[width=6cm]{figures/SPFVar_ab_ashocks.png} 
	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2019}
	\label{ReplicateCoibionwholeperiod}
\end{figure}

>>>>

\begin{figure}[ht]
	\centering
	\includegraphics[width=7cm]{figures/Inf_ashocks_nmp.png}  
	\includegraphics[width=7cm]{figures/Inf_ashocks.png} \\
	\smallskip
	\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp.png} 
	\includegraphics[width=7cm]{figures/SPFFE_ashocks.png} \\
	\smallskip
	\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
	\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks.png} \\
	\smallskip 
	\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks_nmp.png} 
	\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks.png} 
	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2019}
	\label{ReplicateCoibionwholeperiod}
\end{figure}
